Carbon Management Strategies for a Climate-Neutral European Economy

### 2023-12-30 report/submissions/journal/cover_letter/letter.tex
further work on cover letter

%%%%%%%%%%% Put Recommender(your mentor) Information Here %%%%%%%%%%%
%
\def\name{Fabian Hofmann, Christoph Tries, Fabian Neumann, Elisabeth Zeyen, Tom Brown.
}
%
% List your degree(s), licences, etc. here if you like.
%\def\What{, Your degrees, etc.}
%
% Set the name of your Department or School here
% I honestly don't know why the negative spacing is necessary to get the alignment of the first line correct.  This must be a ``\tikz'' thing.
%%%%%%%%%%%%%%%%%%  School or Department %%%%%%%%%%%%%%%
\def\Where{\hspace{-1.2mm}\textbf{\color{tubred}
	Department of Digital\\Transformation in Energy Systems,\\ TU Berlin
}}

@@

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		Thank you for the opportunity to submit our manuscript to Nature Energy. Hereby we submit the paper “\hydrogen{} and \carbon{} Network Strategies for the European Energy System”.

		In our study, we introduce the first large-scale investment model that assesses the co-benefits of a carbon-dioxide and a hydrogen transport system in Europe. The model optimizes the production, transport, and storage of various carriers, including electricity, hydrogen, methane, and carbon-dioxide, across all relevant sectors.

		The paper appears at an important time, with policy makers and industry leaders concretizing plans and investments for hydrogen and carbon-dioxide management systems. In particular, it remains unclear how and to what extent synthetic fuel production and permanent carbon storage (carbon sequestration) should be integrated into the future energy system.

		Our analysis not only confirms the crucial flexibility that \hydrogen{} and \carbon{} transport systems bring to \carbon{} emission neutral energy systems, but also illustrates how their combination further enhances energy efficiency and social welfare. We show that the hydrogen grid optimally transports low-cost hydrogen from areas with good renewable resources to regionally-distributed carbon sources such as industrial clusters and biomass combustion plants to enable synthetic fuel production at site. A carbon-dioxide network, on the other hand, is most cost-beneficial to transport low-cost carbon from point sources near the coast to sequestration sites to permanently store it. In such a setup, the system unlocks most carbon capture potentials from biomass and reduces the reliance on cost-intensive direct air capture. Moreover, the benefits of deploying both networks increase when enforcing a net carbon-removal target, leading to system-cost reductions of 6 billion Euros per year.

		Our analysis underlines the importance of incorporating hydrogen and carbon dioxide networks into European energy policy for a resilient, carbon-neutral or negative future energy system.

		We did not have any prior discussions with a Nature Energy editor about this manuscript. The manuscript has not been published and is not under consideration for publication elsewhere.

		We believe that our findings are in line with the scope of Nature Energy and will be of interest to your readership. We want to thank the editor for taking the time to consider the publication of our paper in Nature Energy.

>>>>

%%%%%%%%%%% Put Recommender(your mentor) Information Here %%%%%%%%%%%
%
\def\name{Dr. Fabian Hofmann,\\Christoph Tries,\\Dr. Fabian Neumann,\\Elisabeth Zeyen,\\Prof. Dr. Tom Brown.
}
%
% List your degree(s), licences, etc. here if you like.
%\def\What{, Your degrees, etc.}
%
% Set the name of your Department or School here
% I honestly don't know why the negative spacing is necessary to get the alignment of the first line correct.  This must be a ``\tikz'' thing.
%%%%%%%%%%%%%%%%%%  School or Department %%%%%%%%%%%%%%%
\def\Where{\hspace{-1.2mm}\textbf{\color{tubred}
	Department of Digital\\Transformation in Energy Systems,\\ TU Berlin
}}

@@

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		Thank you for the opportunity to submit our manuscript to Nature Energy. We are pleased to present our paper titled “\hydrogen{} and \carbon{} Network Strategies for the European Energy System”. This collaborative effort from researchers at the Institute of Energy Technology, Technical University of Berlin, contributes to the critical discourse on climate-neutral energy systems in Europe.

		In our study, we introduce the first large-scale investment model to analyze potential synergies and competition between hydrogen and carbon dioxide transport networks within a carbon-neutral European energy system.  Our model represents an advancement over existing models by optimizing a comprehensive range of technologies for the production, transportation, and storage of various energy carriers across all relevant sectors at high temporal and spatial resolution.

		The publication of this paper is timely, considering that policymakers and industry leaders are currently formulating plans and investments for hydrogen and carbon dioxide management systems. Our study offers critical insights and practical implications for the integration of synthetic fuel production and permanent carbon storage (carbon sequestration) into future energy systems.

		Our analysis not only confirms the role of hydrogen and carbon dioxide transport systems in providing crucial flexibilities to carbon-neutral energy systems. It also illustrates how their combination enhances energy efficiency and social welfare. We demonstrate that a hydrogen grid is optimally used to transport low-cost hydrogen from regions with abundant renewable resources to distributed carbon sources, such as industrial clusters and biomass combustion plants, to enable on-site synthetic fuel production. Conversely, a carbon dioxide network efficiently transports low-cost carbon from point sources near the coast to sequestration sites for permanent storage. Such an approach increase carbon capture rates from biomass combustion and reduces reliance on cost-intensive direct air capture. Furthermore, the benefits of deploying both networks are amplified under a net carbon-removal target.
		As underscored by our analysis, the integration of hydrogen and carbon dioxide networks into European energy policy is vital for a resilient, carbon-neutral, or negative future energy system.

		This manuscript has not been published nor is it under consideration elsewhere. It has not been previously discussed with any Nature Energy editor.

		We believe that our findings align with the scope of Nature Energy and will interest your readership. We appreciate the editor's time in considering our manuscript for publication.
